Reevaluando la Eficacia de los Desafíos de Código: Desmitificando la Idea de un Ingeniero como una IA Omnisciente

### 2023-10-19 CS2324W-OSP-MCS/Reevaluando la Eficacia de los Desafíos de Código/paper.tex
Upload - CS23-00W Papers

% Code Challenge Assessment: A Holistic Approach to Evaluating Engineering Talent
% Author: Felipe Alfonso González
% License: MIT
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\title{Reassessing the Efficacy of Code Challenges: Debunking the Notion of an Engineer as an All-Knowing AI}

@@

PSYCHOLOGICAL ASPECTS OF TECH INTERVIEWS

the importance of having great open source projects : it's a source for different eyes about how someone can handle code and even a whole infrastructure

Junior developers can do a big contribution

——

@@

the big business of the Bootcamps to ‘teach’ about programming and while toy pay them you they assure you don't go through technical interviews or that kind of procedures

>>>>

% ----------------------------------------------
% Author: Felipe Alfonso González
% License: MIT
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\title{Reevaluando la Eficacia de los Desafíos de Código: Desmitificando la Idea de un Ingeniero como una IA Omnisciente}

@@

PSYCHOLOGICAL ASPECTS OF TECH INTERVIEWS 
——

@@
